Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-06-12 manuscript/tables&figures.Rmd
fig legend fix

**Figure 2. Height profiles in growing season climatic conditions, tree heights by crown position, and leaf hydraulic traits** Shown are averages ($\pm$ SD) of daily maxima and minima of (**a**) wind speed, (**b**) relative humidity ($RH$), and (**c**) air temperature ($T_{air}$) averaged over each month of the peak growing season (May-August) from 2016-2018. In these plots, heights are slightly offset for visualization purposes. Also shown is (**d**) 2018 tree heights by canopy position (see Table 2 for codes). In all plots, the dashed horizontal line indicates the 95th percentile of tree heigts in the ForestGEO plot.

>>>>

**Figure 2. Height profiles in growing season climatic conditions and tree heights by crown position** Shown are averages ($\pm$ SD) of daily maxima and minima of (**a**) wind speed, (**b**) relative humidity ($RH$), and (**c**) air temperature ($T_{air}$) averaged over each month of the peak growing season (May-August) from 2016-2018. In these plots, heights are slightly offset for visualization purposes. Also shown is (**d**) 2018 tree heights by canopy position (see Table 2 for codes). In all plots, the dashed horizontal line indicates the 95th percentile of tree heigts in the ForestGEO plot.
